Proposed Solution

### 2016-11-10 Ennan-Proposal/travis.tex
no pdf of main

Driven by the above motivating example, 
we propose an extension to \app that
learns a given training set with pre-knowledge that 
this training set contains some configuration files 
guaranteed to be correct.
Such an extension employs a new algorithm, named version space learning,
to significantly decrease the false positive rate while maintaining 
the detection capability of \app.

>>>>

Driven by the above motivating example, 
we propose an extension to \app that
learns a given training set with pre-knowledge that 
this training set contains some configuration files 
guaranteed to be correct.
Such an extension employs an existsing technique from the machine learning community, named version space learning,
to significantly decrease the false positive rate while maintaining 
the detection capability of \app.
